Uni- and Multivariate Analysis of Dendritic Ca2+ Data

### 2017-07-12 presentation/demo.tex
asd

\title{Multivariate Analysis of Dendritic Ca2+ Data}
\subtitle{In a Stimulus Detection Task}
\date{\today}
%\date{}
\author{Georg Chechelnizki}
\institute{BCCN Berlin}
% \titlegraphic{\hfill\includegraphics[height=1.5cm]{logo.pdf}}

@@

\section{What Has Happened So Far - Univariate Analysis}

\begin{frame}{Psychometric Curve}
\begin{center}
	\begin{figure}
      \includegraphics[scale=0.38]{psychometric.png}
	\end{figure}
	\end{center}

@@

\begin{frame}{ROC-Analysis}
\begin{center}
	\begin{figure}
      \includegraphics[width=0.75\textwidth]{roc_max.png}
	\end{figure}
	\end{center}
\end{frame}

\begin{frame}{DI-Histograms}
\begin{center}
	\begin{figure}
      \includegraphics[width=1.0\textwidth]{DI_hist.png}
	\end{figure}
	\end{center}
\end{frame}

\begin{frame}{$\text{Ca}^{2+}$-Trace of Largest $|\text{DI}|$-Dendrites}
\begin{center}
	\begin{figure}
      \includegraphics[width=1.0\textwidth]{on_vs_off.png}
      \caption*{Near threshold-stimulus ($\approx 1$)}
	\end{figure}
	\end{center}
\end{frame}

\begin{frame}
placeholder SI-stuff
\end{frame}

\section{Titleformats}

\begin{frame}{Metropolis titleformats}
	\themename supports 4 different titleformats:
	\begin{itemize}
		\item Regular
		\item \textsc{Smallcaps}
		\item \textsc{allsmallcaps}
		\item ALLCAPS
	\end{itemize}
	They can either be set at once for every title type or individually.
\end{frame}

{
    \metroset{titleformat frame=smallcaps}
\begin{frame}{Small caps}
	This frame uses the \texttt{smallcaps} titleformat.

	\begin{alertblock}{Potential Problems}
		Be aware, that not every font supports small caps. If for example you typeset your presentation with pdfTeX and the Computer Modern Sans Serif font, every text in smallcaps will be typeset with the Computer Modern Serif font instead.
	\end{alertblock}
\end{frame}
}

{
\metroset{titleformat frame=allsmallcaps}
\begin{frame}{All small caps}
	This frame uses the \texttt{allsmallcaps} titleformat.

	\begin{alertblock}{Potential problems}
		As this titleformat also uses smallcaps you face the same problems as with the \texttt{smallcaps} titleformat. Additionally this format can cause some other problems. Please refer to the documentation if you consider using it.

		As a rule of thumb: Just use it for plaintext-only titles.
	\end{alertblock}
\end{frame}
}

{
\metroset{titleformat frame=allcaps}
\begin{frame}{All caps}
	This frame uses the \texttt{allcaps} titleformat.

	\begin{alertblock}{Potential Problems}
		This titleformat is not as problematic as the \texttt{allsmallcaps} format, but basically suffers from the same deficiencies. So please have a look at the documentation if you want to use it.
	\end{alertblock}
\end{frame}
}

\section{Elements}

\begin{frame}[fragile]{Typography}
      \begin{verbatim}The theme provides sensible defaults to
\emph{emphasize} text, \alert{accent} parts
or show \textbf{bold} results.\end{verbatim}

  \begin{center}becomes\end{center}

  The theme provides sensible defaults to \emph{emphasize} text,
  \alert{accent} parts or show \textbf{bold} results.
\end{frame}

\begin{frame}{Font feature test}
  \begin{itemize}
    \item Regular
    \item \textit{Italic}
    \item \textsc{SmallCaps}
    \item \textbf{Bold}
    \item \textbf{\textit{Bold Italic}}
    \item \textbf{\textsc{Bold SmallCaps}}
    \item \texttt{Monospace}
    \item \texttt{\textit{Monospace Italic}}
    \item \texttt{\textbf{Monospace Bold}}
    \item \texttt{\textbf{\textit{Monospace Bold Italic}}}
  \end{itemize}
\end{frame}

\begin{frame}{Lists}
  \begin{columns}[T,onlytextwidth]
    \column{0.33\textwidth}
      Items
      \begin{itemize}
        \item Milk \item Eggs \item Potatos
      \end{itemize}

    \column{0.33\textwidth}
      Enumerations
      \begin{enumerate}
        \item First, \item Second and \item Last.
      \end{enumerate}

    \column{0.33\textwidth}
      Descriptions
      \begin{description}
        \item[PowerPoint] Meeh. \item[Beamer] Yeeeha.
      \end{description}
  \end{columns}
\end{frame}
\begin{frame}{Animation}
  \begin{itemize}[<+- | alert@+>]
    \item \alert<4>{This is\only<4>{ really} important}
    \item Now this
    \item And now this
  \end{itemize}
\end{frame}
\begin{frame}{Figures}
  \begin{figure}
    \newcounter{density}
    \setcounter{density}{20}
    \begin{tikzpicture}
      \def\couleur{alerted text.fg}
      \path[coordinate] (0,0)  coordinate(A)
                  ++( 90:5cm) coordinate(B)
                  ++(0:5cm) coordinate(C)
                  ++(-90:5cm) coordinate(D);
      \draw[fill=\couleur!\thedensity] (A) -- (B) -- (C) --(D) -- cycle;
      \foreach \x in {1,...,40}{%
          \pgfmathsetcounter{density}{\thedensity+20}
          \setcounter{density}{\thedensity}
          \path[coordinate] coordinate(X) at (A){};
          \path[coordinate] (A) -- (B) coordinate[pos=.10](A)
                              -- (C) coordinate[pos=.10](B)
                              -- (D) coordinate[pos=.10](C)
                              -- (X) coordinate[pos=.10](D);
          \draw[fill=\couleur!\thedensity] (A)--(B)--(C)-- (D) -- cycle;
      }
    \end{tikzpicture}
    \caption{Rotated square from
    \href{http://www.texample.net/tikz/examples/rotated-polygons/}{texample.net}.}
  \end{figure}
\end{frame}
\begin{frame}{Tables}
  \begin{table}
    \caption{Largest cities in the world (source: Wikipedia)}
    \begin{tabular}{lr}
      \toprule
      City & Population\\
      \midrule
      Mexico City & 20,116,842\\
      Shanghai & 19,210,000\\
      Peking & 15,796,450\\
      Istanbul & 14,160,467\\
      \bottomrule
    \end{tabular}
  \end{table}
\end{frame}
\begin{frame}{Blocks}
  Three different block environments are pre-defined and may be styled with an
  optional background color.

  \begin{columns}[T,onlytextwidth]
    \column{0.5\textwidth}
      \begin{block}{Default}
        Block content.
      \end{block}

      \begin{alertblock}{Alert}
        Block content.
      \end{alertblock}

      \begin{exampleblock}{Example}
        Block content.
      \end{exampleblock}

    \column{0.5\textwidth}

      \metroset{block=fill}

      \begin{block}{Default}
        Block content.
      \end{block}

      \begin{alertblock}{Alert}
        Block content.
      \end{alertblock}

      \begin{exampleblock}{Example}
        Block content.
      \end{exampleblock}

  \end{columns}
\end{frame}
\begin{frame}{Math}
  \begin{equation*}
    e = \lim_{n\to \infty} \left(1 + \frac{1}{n}\right)^n
  \end{equation*}
\end{frame}
\begin{frame}{Line plots}
  \begin{figure}
    \begin{tikzpicture}
      \begin{axis}[
        mlineplot,
        width=0.9\textwidth,
        height=6cm,
      ]

        \addplot {sin(deg(x))};
        \addplot+[samples=100] {sin(deg(2*x))};

      \end{axis}
    \end{tikzpicture}
  \end{figure}
\end{frame}
\begin{frame}{Bar charts}
  \begin{figure}
    \begin{tikzpicture}
      \begin{axis}[
        mbarplot,
        xlabel={Foo},
        ylabel={Bar},
        width=0.9\textwidth,
        height=6cm,
      ]

      \addplot plot coordinates {(1, 20) (2, 25) (3, 22.4) (4, 12.4)};
      \addplot plot coordinates {(1, 18) (2, 24) (3, 23.5) (4, 13.2)};
      \addplot plot coordinates {(1, 10) (2, 19) (3, 25) (4, 15.2)};

      \legend{lorem, ipsum, dolor}

      \end{axis}
    \end{tikzpicture}
  \end{figure}
\end{frame}
\begin{frame}{Quotes}
  \begin{quote}
    Veni, Vidi, Vici
  \end{quote}
\end{frame}

{%
\setbeamertemplate{frame footer}{My custom footer}
\begin{frame}[fragile]{Frame footer}
    \themename defines a custom beamer template to add a text to the footer. It can be set via
    \begin{verbatim}\setbeamertemplate{frame footer}{My custom footer}\end{verbatim}
\end{frame}
}

\begin{frame}{References}
  Some references to showcase [allowframebreaks] \cite{knuth92,ConcreteMath,Simpson,Er01,greenwade93}
\end{frame}

\section{Conclusion}

\begin{frame}{Summary}

  Get the source of this theme and the demo presentation from

  \begin{center}\url{github.com/matze/mtheme}\end{center}

  The theme \emph{itself} is licensed under a
  \href{http://creativecommons.org/licenses/by-sa/4.0/}{Creative Commons
  Attribution-ShareAlike 4.0 International License}.

  \begin{center}\ccbysa\end{center}

{\setbeamercolor{palette primary}{fg=black, bg=yellow}
\begin{frame}[standout]
  Questions?
\end{frame}
}

\appendix

\begin{frame}[fragile]{Backup slides}
  Sometimes, it is useful to add slides at the end of your presentation to
  refer to during audience questions.

  The best way to do this is to include the \verb|appendixnumberbeamer|
  package in your preamble and call \verb|\appendix| before your backup slides.

  \themename will automatically turn off slide numbering and progress bars for
  slides in the appendix.
\end{frame}

\begin{frame}[allowframebreaks]{References}

  \bibliography{demo}
  \bibliographystyle{abbrv}

>>>>

\title{Uni- and Multivariate Analysis of Dendritic Ca2+ Data}
\subtitle{In a Stimulus Detection Task}
\date{\today}
%\date{}
\author{Georg Chechelnizki}
\institute{BCCN Berlin}
% \titlegraphic{\hfill\includegraphics[height=1.5cm]{logo.pdf}}

@@

\begin{frame}[fragile]{The Data - Psychometric Curve}
\begin{center}
	\begin{figure}
      \includegraphics[scale=0.38]{psychometric.png}
	\end{figure}
	\end{center}

@@

\section{Goal}
\begin{frame}[fragile]{Goal}
The goal of this project is to investigate the following:
\begin{itemize}
\only<+->{
\item What information can we extract from the data?}
\only<+->{
\item What can we gain by doing multivariate analysis as opposed to univariate?}
\only<+->{
\item Can we say something about population coding?}
\end{itemize}
\end{frame}

\section{Univariate Analysis}

\begin{frame}[fragile]{Stimulus Presence Detection}
\begin{itemize}
\item Feature: mean activity of dendrite over one second after stimulus
\item Class one: all trials with stimulus strength 0
\item Class two: all trials with selected stimulus strength $(\neq 0)$
\end{itemize}
\end{frame}

\begin{frame}[fragile]{ROC}
\begin{center}
	\begin{figure}
      \includegraphics[width=0.75\textwidth]{roc_max.png}
	\end{figure}
	\end{center}
\end{frame}

%\begin{frame}[fragile]{Distribution of DI-Values}
%\begin{center}
%	\begin{figure}
%      \includegraphics[width=1.0\textwidth]{DI_hist.png}
%	\end{figure}
%	\end{center}
%\end{frame}
%
%\begin{frame}[fragile]{Distribution of DI-Values vs. Chance}
%\begin{center}
%	\begin{figure}
%      \includegraphics[width=1.0\textwidth]{realchance.png}
%	\end{figure}
%	\end{center}
%\end{frame}

\begin{frame}[fragile]{$\text{Ca}^{2+}$-Trace of Largest $|\text{DI}|$-Dendrites}
\begin{center}
	\begin{figure}
      \includegraphics[width=1.0\textwidth]{on_vs_off.png}
      \caption*{Near threshold-stimulus ($\approx 1$)}
	\end{figure}
	\end{center}
\end{frame}

%\begin{frame}[fragile]{ROC Scores of Single Dendrites Using SVM}
%\begin{table}
%    \caption*{Stimulus strength 1 (near thereshold). Something is fishy here}
%    \begin{tabular}{c|c|c}
%      \toprule
%      Dendrite \# & Mean Accuracy & Standard Deviation\\
%      \midrule
%      57 & 0.44 & +/- 0.51\\
%      53 & 0.40 & +/- 0.28\\
%      48 & 0.38 & +/- 0.49\\
%      2 & 0.37 & +/- 0.74\\
%      \bottomrule
%    \end{tabular}
%  \end{table}
%\end{frame}

\begin{frame}[fragile]{SVM - Most Accurate Dendrites}
\begin{table}
    \caption*{Stimulus strength 1 (near thereshold)}
    \begin{tabular}{c|c|c}
      \toprule
      Dendrite \# & $\mu_{acc}$ & $\sigma_{acc}$\\
      \midrule
      57 & 0.70 & 0.12\\
      53 & 0.68 & 0.14\\
      48 & 0.63 & 0.13\\
      27 & 0.62 & 0.08\\
      \bottomrule
    \end{tabular}
  \end{table}
\end{frame}

\begin{frame}[fragile]{Rank Order Correlations of Dendrites Over Stimuli}
\begin{center}
	\begin{figure}\caption*{Weighted rank coefficient $\rho_{\omega}$ (todo: find more optimal weights)}
      \includegraphics[width=1.0\textwidth]{rank_presence.png}
	\end{figure}
	\end{center}
\end{frame}

\begin{frame}[fragile]{DI and SVM Dendrtie Rank Order Correlation}
\begin{center}
	\begin{figure}
	\caption*{Something is wrong here, should be more correlation}
      \includegraphics[width=1.0\textwidth]{DI_vs_SVM.png}
	\end{figure}
	\end{center}
\end{frame}

\begin{frame}[fragile]{Tuning Curves}
\begin{center}
	\begin{figure}
      \includegraphics[width=1.0\textwidth]{tuning.png}
	\end{figure}
	\end{center}
\end{frame}

\begin{frame}[fragile]{Tuning Curves}
\begin{center}
	\begin{figure}
      \includegraphics[width=1.0\textwidth]{tuning_ca2+.png}
      \caption*{todo:accuracies}
	\end{figure}
	\end{center}
\end{frame}

\begin{frame}[fragile]{Behavoreal Prediction - Most Accurate Dendrites}
\begin{table}
    \caption*{Stimulus strength 1 (near thereshold)}
    \begin{tabular}{c|c|c}
      \toprule
      Dendrite \# & Mean Accuracy & Standard Deviation\\
      \midrule
      70 & 0.78 & +/- 0.28\\
      47 & 0.77 & +/- 0.32\\
      56 & 0.73 & +/- 0.24\\
      92 & 0.70 & +/- 0.33\\
      \bottomrule
    \end{tabular}
  \end{table}
\end{frame}

\begin{frame}[fragile]{Behavoreal Tuning}
\begin{center}
	\begin{figure}
      \includegraphics[width=1.0\textwidth]{tuning_ca2+_bb.png}
      \caption*{todo:accuracies}
	\end{figure}
	\end{center}
\end{frame}

\begin{frame}[fragile]{Rank Correlations of Behavoreal and Presence Dendrites}
\begin{center}
	\begin{figure}
	\caption*{reduce ndends}
      \includegraphics[width=1.0\textwidth]{transrank.png}
	\end{figure}
	\end{center}
\end{frame}

\section{Multivariate SMV Analysis}

\begin{frame}[fragile]{SVM Performance on Combined Dendrites}
Placeholder - Something wrong when using other files!
\end{frame}

\begin{frame}[fragile]{SVM Performance on Combined Dendrites - Behavoreal}
Placeholder - Something wrong when using other files!
\end{frame}

\begin{frame}[fragile]{Optimal Averaging Times}
\begin{center}
	\begin{figure}
	\caption*{Solve Problem with combined SVM first}
      \includegraphics[width=1.0\textwidth]{placeholder_wind_pres.png}
	\end{figure}
	\end{center}
\end{frame}

\begin{frame}[fragile]{Optimal Averaging Times - Behavior}
\begin{center}
	\begin{figure}
	\caption*{Solve Problem with combined SVM first}
      \includegraphics[width=1.0\textwidth]{placeholder_wind_hit.png}
	\end{figure}
	\end{center}
\end{frame}

\begin{frame}[fragile]{Mante - Approach (Placeholder Title)}
Math goes here
\end{frame}

\begin{frame}[fragile]{Mante - Approach - Results}
\begin{center}
	\begin{figure}
	\caption*{Solve Problem with combined SVM first}
      \includegraphics[width=1.0\textwidth]{reg_norm_placeholder.png}
	\end{figure}
	\end{center}
\end{frame}

\begin{frame}[fragile]{Mante - Approach - Results}
\begin{center}
	\begin{figure}
	\caption*{Solve Problem with combined SVM first}
      \includegraphics[width=1.0\textwidth]{reg_inte_placeholder.png}
	\end{figure}
	\end{center}
\end{frame}
